---
title: "Assignment Week 6 ANOVA"
output:
  pdf_document: default
  html_notebook: default
---

```{r import-library}
library(tidyverse)
library(dplyr)
library(knitr)
library(kableExtra)
library(rstatix)
library(ggpubr)
library(lsr)
library(papaja)
theData <- as.data.frame(read.csv("./PSYC20007_data_2020.csv"))
str(theData)
theData$Language.classification <- factor(theData$Language.classification, ordered = FALSE, levels = c("mono", "slc", "dlc"))
levels(theData$Language.classification) <- c("Monolingual","Single language context","Dual language context")
str(theData)
```

```{r descriptives}
longData <- theData %>% 
  pivot_longer(cols = c("Flanker.effect","No.go.accuracy"), names_to = "task", values_to = "value")
str(longData)
summarytable <- longData %>%
  group_by(task, Language.classification) %>%
  dplyr::summarise(
    mean = mean(value),
    sem = sd(value)/sqrt(n()),
    sd = sd(value),
    min = min(value),
    max = max(value),
    n = n()) %>%
ungroup() 
kable(t(summarytable)
  , caption = "Descriptive statistics of score by language classification."
)
papaja::apa_table(summarytable  , caption = "Descriptive statistics of value  by language classification"
  , note = "This table was created with apa_table()."
  , escape = TRUE
)


```


```{r check-assumptions}
# check if we can do ANOVA

levels(longData$Language.classification)
longData %>% ggplot( aes(x=Language.classification, y=value)) + 
    geom_violin(draw_quantiles = 1) +
  facet_wrap(~task, scales = "free")


flankerplot <- ggline(theData, x = "Language.classification", y = "Flanker.effect",
       add = c("mean_ci", "jitter", "violin"), 
     #  error.plot = "linerange",
       order = c("Monolingual", "Single language context", "Dual language context"),
       ylab = "Flanker effect", xlab = "Language Classification")
ggpar(flankerplot, )

nogoplot <- ggline(theData, x = "Language.classification", y = No.go.accuracy,
       add = c("mean_ci", "jitter", "violin"), 
     #  error.plot = "linerange",
       order = c("Monolingual", "Single language context", "Dual language context"),
       ylab = "No-go accuracy (%)", xlab = "Language Classification")
ggpar(nogoplot, )


longData %>% 
  group_by(task, Language.classification) %>%
  identify_outliers(value) %>%
  ungroup()

levels(theData$Language.classification)

model.Flanker <- lm(Flanker.effect ~ Language.classification, data = theData)
ggqqplot(residuals(model.Flanker))

theData %>%
  group_by(Language.classification) %>%
  rstatix::shapiro_test(Flanker.effect) %>%
  ungroup()

ggqqplot(theData, "Flanker.effect", facet.by ="Language.classification",title = "QQ plot by group: Flanker effect")

model.Nogo <- lm(No.go.accuracy ~ Language.classification, data = theData)
ggqqplot(residuals(model.Nogo))

theData %>%
  group_by(Language.classification) %>%
  rstatix::shapiro_test(No.go.accuracy) %>%
  ungroup()

ggqqplot(theData, "No.go.accuracy", facet.by ="Language.classification", title = "QQ plot by group: No-go accuracy")


```

# Homogenity of variance
A residuals versus fits plot can be used to check the homogeneity of variances.
 Levene's tests showing $p$ > $0.05$ show that there is no significant difference between  variances across groups.

```{R homogenity}
plot(model.Flanker, 1)
theData %>% levene_test(Flanker.effect ~ Language.classification)
plot(model.Nogo, 1)
theData %>% levene_test(No.go.accuracy ~ Language.classification)
```
## ANOVA

```{R anova}
aov_flanker <- aov(data = theData, 
                   formula = Flanker.effect ~ Language.classification)
summary(aov_flanker)
aov_nogo <- aov(data = theData, 
                   formula = No.go.accuracy ~ Language.classification)
summary(aov_nogo)
aov_flankera <- apa_print(aov_flanker)
aov_nogoa <- apa_print(aov_nogo)

apa_table(list(aov_flankera$table, aov_nogoa$table), caption = "ANOVA for two dependant variables", note = "the note goes here")
```

Here we use `apa_print` to report the statistic and `eta_squared` for $\eta ^2$. Flanker: 
`r apa_print(aov_flanker)$statistic`, $\eta ^2 = `r eta_squared(aov_flanker)`$ ; No go: `r apa_print(aov_nogo)$statistic`, $\eta ^2 = `r eta_squared(aov_nogo)`$.


## Effect size 

```{R etaSquared}
etaSquared(aov_flanker, anova=FALSE)
etaSquared(aov_nogo, anova=FALSE)
```



## Post Hoc Tests

### Tukey (won't be used in document)

```{R Tukey}
tuk_flanker <- TukeyHSD(aov_flanker)
tuk_flanker

tuk_nogo <- TukeyHSD(aov_nogo)
tuk_nogo
```

```
